\documentclass[line, margin]{res}

\begin{document}
\name{Suraj Tripathi}
\address{ +91 9833471993, surajtripathi793@gmail.com}
\begin{resume}

\section{EXPERIENCE} 
\textbf{Senior Backend Engineer (SDE-3), Gitlab, Remote \hfill Jan'22 - Present} \\
\begin{enumerate}
  \item Mentored junior members to promotion.
  \item Worked with Product managers in KR definition and for tracking progressions.
  \item Partnered with Product Managers in quarter planning as an Engineering counterpart.
  \item Performed agile sprint planning and management for the team.
  \item Worked on various projects as part of the Utilization team in the Fulfillment Department.
  \begin{itemize}
    \item Storage utilization and enforcement of limitations on Gitlab for Free users
    \item Delivered NonBillable to Billable Promotion Mgmt from MVP to Feature Complete.
    \item Promotion Management and Block Seat Overages for SAML, LDAP, SCIM integrations.
  \end{itemize}
  \item Resolved multiple customer issues to keep error budgets in check.
\end{enumerate}
\textbf{\textit{Technologies used : }} Ruby on Rails, Go, Postgres\\
\\
\textbf{Team Lead, Browserstack, India \hfill Apr'21 - Jan-22} \\
\textbf{Senior Software Engineer, Browserstack, India \hfill Apr'19 - Mar'21} \\
\textbf{Software Engineer, Browserstack, India \hfill Dec'17 - Mar'19} \\
\begin{enumerate}
   \item Leading AppLive product and managing Sprints, Planning and OKR Execution within the team.
   \item Core Mobile OS Feature Support
   \begin{itemize}
     \item Add support for Devtools on IOS
     \item Support for IP and GPS GeoLocation
     \item Biometric Authentication on Android
     \item Built tool to allow users to access iOS Settings
   \end{itemize}
   \item Insession Product Management tools integration
   \item Device Cleanup Service Rewrite
   \item App Upload time optimization
   \item Reduce Session Start Time for IOS from 25sec to 7 sec
   \item Scaled internal Log Pusher service to handle 5x more traffic
   \item Built Sales Target Dashboard for Internal Consumption
\end{enumerate}
\textbf{\textit{Technologies used : }} Ruby on Rails, Node Js, Objective C,BigQuery, Python, MySql\\
\\
\textbf{Software Engineer, TranServ, India \hfill Aug'16 - Nov'17} \\
\textbf{\textit{``Udio Wallet"}} \\
Worked to build a wallet framework Udio2.0(Java) from scratch and to migrate all of the core functionalities and data of Udio1.0 framework(php). \\
Worked on various Partner API's which provide Debit, Credit, Reporting Functionalities.\\
\textbf{\textit{Technologies used : }} Java, Redis, Mysql, Javascript \\
\\
\textbf{Software Engineer , Mobileum, India \hfill Feb'15 - July'16} \\
\textbf{\textit{``iCampaign 1.0"}} \\
Worked to build Generic rule based campaign pushing sms-framework.\\
Took ownership of the rule-engine framework which allowed configuration of complex business rules to target users. \\
Added AB Testing feature in the iCampaign framework.\\
Worked on USSD response framework for Telecom partners which would allow querying of Roaming plans and activation of the same.\\
\textbf{\textit{Technologies used : }} Java, Oracle \\
\\

\section{SKILLS} 
\textbf{Languages : }Java(Good), Nodejs (Good), C(Good), C++(Good), Python(Good), Ruby(Good), Javascript(Good), \\HTML(Acquainted), CSS(Acquainted), Objective-C(Acquainted) \\
\textbf{Frameworks : }Rails, Express, Django, Spring, Hibernate, Mybatis, JDBC \\
\textbf{Databases : }Mysql, Oracle, Redis, Mongodb, BigQuery, Postgresql \\
\textbf{Tools : }Sublime, WebStorm, IntelliJ, Eclipse, Maven, Git, Tomcat, Postman, JIRA, Asana \\
\textbf{Systems : }Linux, Windows, Mac-Os

\section{EDUCATION} 
\textbf{\textit{CDAC, PG Diploma in Advance Computing} \hfill Aug'14-Jan'15} \\
Vidyanidhi Infotech, Juhu \\
Percentage Obtained: 80\% \\
\\
\textbf{\textit{BE Computer Science} \hfill Aug'10-Jun'14} \\
University Of Mumbai \\
Percentage Obtained : 67\% \\
\section{HONORS}
\textbf{\textit{Udio Star Performer Of the Month.} \hfill Sept-2016} \\ 
\textbf{\textit{Most Valued Person, Mobileum.} \hfill Oct-2015} \\ 
\section{PERSONAL PROFILE}

\textbf{\textit{Linkedin.}} https://www.linkedin.com/in/surajtripathi793 \\
\textbf{\textit{GitHub.}} https://github.com/surajtripathy07  \\
\textbf{\textit{Personal Website.}} https://surajtripathi.info\\
\end{resume}
\end{document}
